Symbolic Abstract Data Type Inference

### 2015-07-06 motivation.tex
Quick typo fix.

\begin{figure}
  \begin{verbatim}
procedure INFER_ADT_FROM_REFERENCE_IMPL(I)
  PATTERNS := {}
  for each sequential history H
    if * then
      break
    else if H is EXECUTABLE with I then
      continue
    else if H is REDUNDANT with PATTERNS then
      continue
    else
      add H to PATTERNS
    end
  end
  return EXCLUSION of PATTERNS
  \end{verbatim}
  \caption{An abstract algorithm for symbolic ADT inference.}
  \label{fig:abstract}
\end{figure}

>>>>

\begin{figure}
  \begin{verbatim}
procedure INFER_ADT_FROM_REFERENCE_IMPL(I)
  PATTERNS := {}
  for each sequential history H
    if * then
      break
    else if H is EXECUTABLE with I then
      continue
    else if H is REDUNDANT with PATTERNS then
      continue
    else
      add H to PATTERNS
    end
  end
  return EXCLUSION of PATTERNS
end
  \end{verbatim}
  \caption{An abstract algorithm for symbolic ADT inference.}
  \label{fig:abstract}
\end{figure}
